Supplementary Information

### 2020-10-08 writing/transect_supplement.Rmd
caption for quality check figure

(ref:qual-check-s) Read quality profiles for different sequencing strategies

(ref:qual-check) **(a)** per-base error rate; **(b)** expected number of errors per read, with threshold of 3 expected errors marked as a dashed vertical line. Statistics are based on quality scores assigned by technology-specific basecallers.

```{r qual-check, fig.cap = "(ref:qual-check-s). (ref:qual-check)", fig.scap = "(ref:qual-check-s)",fig.height=6}
ggpubr::ggarrange(
  readd(erate_plot),
  readd(eexp_plot),
  readd(eexp_region_plot),
  ncol = 1,
  # common.legend = TRUE,
  # legend = "bottom",
  labels = "auto"
)
```

>>>>

(ref:qual-check-s) Read quality profiles

(ref:qual-check) based on quality scores assigned by technology-specific basecallers. **(a)** per-base error rate for different sequencing strategies; **(b)** expected number of errors per read for different sequencing strategies; **(c)** expected number of errors per read for regions extracted from PacBio long amplicon reads. In **(a)** and **(b)**, R1 and R2 denote the forward and reverse reads, respectively, from Illumina paired-end sequencing.  PacBio short, Ion Torrent, and Illumina datasets were all sequenced from the same short amplicon library.  In **(b)** and **(c)**, quality filtering threshold of 3 expected errors marked as a dashed vertical line.

```{r qual-check, fig.cap = "(ref:qual-check-s), (ref:qual-check)", fig.scap = "(ref:qual-check-s)",fig.height=7}
ggpubr::ggarrange(
  readd(erate_plot),
  readd(eexp_plot),
  readd(eexp_region_plot),
  ncol = 1,
  # common.legend = TRUE,
  # legend = "bottom",
  labels = "auto"
)
```
